

```{r}
df = read.csv("C://Users/dunga/species-dist-modeling/by_habitat/ranunculus.tsv", sep="\t")
df
```

```{r}
df = df[,c("Scientific.name", "WGS84.E", "WGS84.N")]
colnames(df) = c("species", "longitude", "latitude")
df
```

```{r}
write.csv(df, "C://Users/dunga/species-dist-modeling/by_habitat/ranunculus-clean.csv", row.names = F)
```

```{r}
library(dismo) # interface with MaxEnt
library(raster) # spatial data manipulation
library(MASS) # for 2D kernel density function
library(magrittr) # for piping functionality, i.e., %>%
library(maptools) # reading shapefiles
library(rJava)
``````


```{r}
elev = raster("C://Users/dunga/species-dist-modeling/env-rasters/wc2.1_5m_elev.tif")
finland = readShapePoly("C://Users/dunga/Downloads/stanford-mb800bj2863-shapefile/mb800bj2863.shp")
elev_finland = mask(elev, finland) %>% crop(finland)
```

```{r}
png("C://Users/dunga/species-dist-modeling/plots/elev.png")
plot(elev_finland, main="Elevation map of Finland")
dev.off()

```
```{r}
writeRaster(elev_finland, "C://Users/dunga/species-dist-modeling/env-rasters/elev.grd")
```
```{r}
ranunculus = raster("C://Users/dunga/species-dist-modeling/by_habitat/out/Ranunculus_glacialis.asc")
png("C://Users/dunga/species-dist-modeling/plots/ranunculus.png")
plot(ranunculus, terrain.colors(255), main="Ranunculus glacialis")
dev.off()
```

```{r}
plot(raster("C://Users/dunga/species-dist-modeling/env-rasters/bio10.grd"))
```

